## 1. Preparation

```{r checkwd}
# getwd()
```

```{r packages}
library(dplyr)
#install.packages("labelled") for labelled data
library(labelled)
# install.packages("survey") # for survey design
library(survey)
# install.packages("car")
library(car)
#install.packages ("forestplot")
library(forestplot)
#install.packages("jtools")
library(jtools)
#install.packages("MASS")
library(MASS)
# install.packages ("caret")
library(caret)
```

## 2. Load data

```{r load}
### 26/1 newly saved RData file has all objects
load("tp.RData") # Given that STATA datasets are already saved inside RData
```

## 3. Extraction

### 3.1 From Individual Recode file

```{r extract_ir}
## extract selected variables from IR
ir_data <- ir %>% dplyr::select(1:8, # ID and weight
                        c( v012,v013, # age
                        v021,v023, # cluster(psu), strata (region*ur)
                        v024,v025, # place
                        v102, v104,v105,v175, # migration status
                        v106, v190, v731, # edu, wealth, employment
                        v201, v213, v245, # pregnancy history for calculation
                        v225, v485a, # wantedness, alcohol,  
                        v304_01:v304_20, v313, v362,# contraception knowledge, current use, intention to use in future
                        v501, #current marital status
                        v701, v730,# partner age, education
                        p32_01:p32_20, # pregnancy outcomes
                        v531,v511, # Age at first sex/marriage
                        v384a:v384h, # exposure to family planning messages
                        v467b, v467c, v467d, v467f # problem access to health services
                      ))
```

### 3.2 From Household Recode file

```{r extract_hr}
## extract selected variables from HR
hr_data <- hr %>% dplyr::select(1:7,
                         c(hv109_01:hv109_56,# highest education attained in the HH
                           hv005, hv021,hv023, # weight, cluster(psu), strata (region*ur)
                           hv012, # total number of HH members
                           hv219 # sex of hh head
                         )) 
```

## 4. Recode files

### 4.1 Recode IR file

```{r recode_ir}
### teenage pregnancy recode - outcome 1 = Yes, 0 = No 
ir_data <- ir_data %>% mutate(
  v013 = factor(v013),
  teen_preg = ifelse(v013 == 1 & (v201 > 0 | v245 > 0 | v213 == 1), 1, 0))
ir_data %>% group_by(teen_preg) %>% summarise(n = n()) # check grouping

### current employment - covariate 1 = Yes, 0 = No
ir_data <- ir_data %>% mutate(
  employ_current = ifelse(v731 %in% c(2,3), 1, 0))
table(ir_data$employ_current,ir_data$v731) # check grouping

### knowledge on any contraceptive method - covariate 1 = Yes, 0 = No
ir_data <- ir_data %>% mutate(
  contra_know_any = ifelse(v304_01== 1 | v304_02== 1 | v304_03== 1 | v304_04== 1 | v304_05== 1 |
                             v304_06== 1 | v304_07== 1 | v304_08== 1 | v304_09== 1 | v304_10== 1 |
                             v304_11== 1 | v304_12== 1 | v304_13== 1 | v304_14== 1 | v304_15== 1 |
                             v304_16== 1 | v304_17== 1 | v304_18== 1 | v304_19== 1 | v304_20== 1, 1, 0))
ir_data %>% group_by(contra_know_any) %>% summarise(n = n()) # check grouping

### current contraceptive use - covariate 1 = Yes, 0 = No
ir_data <- ir_data %>% mutate(
  contra_current = ifelse(v313 %in% c(1,2,3), 1, 0))
table(ir_data$contra_current,ir_data$v313) # check grouping

### intention to use contraception in the future - covariate 1 = Yes, 0 = No
ir_data <- ir_data %>%  mutate(
    contra_future = case_when(
      is.na(v362) ~ NA_real_,  # Preserve NA values
      v362 %in% c(2, 4) ~ 1,   # Assign 1 when v362 is 2 or 4
      TRUE ~ 0                 # Assign 0 otherwise
    ))
table(ir_data$contra_future,ir_data$v362, useNA = "always") # check grouping

### marital status recode from 5 to 3 categories
ir_data <- ir_data %>% mutate(
    marital = dplyr::recode(v501, `0` = "0", `1` = "1", `2` = "1",
                            `3` = "2", `4` = "2", `5` = "2"))
table(ir_data$marital,ir_data$v501, useNA = "always") # check grouping

### education status regroup
ir_data <- ir_data %>% mutate(
    edu_gp = dplyr::recode(v106, `0` = "0", `1` = "1", `2` = "2", `3` = "2")) # 8 > NA is not coded as there is no 8
table(ir_data$edu_gp,ir_data$v106, useNA = "always") # check grouping

### number of live birth regroup
ir_data <- ir_data %>% mutate(
  birth_gp = case_when(
      v201 == 0 ~ "0",
      v201 == 1 ~ "1",
      v201 >= 2 ~ "2"))
table(ir_data$birth_gp,ir_data$v201, useNA = "always") # check grouping

### number of pregnancy loss regroup
ir_data <- ir_data %>% mutate(
  loss_gp = case_when(
      v245 == 0 ~ "0",
      v245 == 1 ~ "1",
      v245 >= 2 ~ "2"))
table(ir_data$loss_gp,ir_data$v245, useNA = "always") 

### age at first sex recode to recode 0, 97, 98 to na
ir_data <- ir_data %>% 
  mutate(v531 = ifelse(v531 %in% c(0, 97, 98), NA, v531))
summary(ir_data$v531) # check range

### age of partner recode to recode 98 to na
ir_data <- ir_data %>% 
  mutate(v730 = ifelse(v730 %in% c(98), NA, v730)) # 10 with more than 90 but included

### partner education recode 8 to na
ir_data <- ir_data %>% 
  mutate(v701 = ifelse(v701 == 8, NA, ifelse (v701 %in% c(2,3), 2, v701)))
ir_data %>% group_by(v701) %>% summarize (n = n()) # check range

### access to informaiton about family planning - covariate 1 = Yes, 0 = No
ir_data <- ir_data %>% mutate(
  fp_info = ifelse(v384a == 1 | v384b == 1 | v384c == 1 | v384d == 1 | 
                     v384e == 1 | v384f == 1 | v384g == 1 | v384h == 1, 1, 0))
ir_data %>% group_by(fp_info) %>% summarise(n = n()) # check grouping
# alternative: data %>% group_by(v384a,v384b,v384c,v384d,v384e,v384f,v384g,v384h) %>% summarize (count = n())

### Create varaible for marital and sex status
ir_data <- ir_data %>%
  mutate(premaritalsex = factor(
      case_when(is.na(v531) | is.na(v511) ~ 2, v531 < v511 ~ 1, TRUE ~ 0),
      levels = c(0, 1, 2),
      labels = c("No", "Yes", "Extraunion sex")))
ir_data %>% filter(teen_preg == 1) %>% 
  group_by(premaritalsex) %>% summarize(n()) # check numbers

## migration within previous 5 year
ir_data <- ir_data %>% mutate(recent_migrate = ifelse(v104 < 5,1,0)) 
ir_data %>% group_by(recent_migrate) %>% summarize (n()) # check numbers

## type of migration (can analyse only when filter for recently migrated***)
ir_data <- ir_data %>% mutate(type_migrate = case_when(
  v102 == 1 & v105 %in% c(0, 1, 2) ~ 1,
  v102 == 1 & v105 == 3 ~ 2,
  v102 == 2 & v105 %in% c(0, 1, 2) ~ 3,
  v102 == 2 & v105 == 3 ~ 4,
    TRUE ~ NA_integer_
)) 
ir_data %>% filter(recent_migrate ==1) %>%
  group_by(type_migrate) %>% summarize (n()) # check numbers
```

### 4.2 Recode HR file

```{r recode_hr}
### recode hh education 98 to na
hr_data <- hr_data %>%
  mutate(across(starts_with("hv109_"), ~ifelse(. == 98, NA, .)))
summary(hr_data$hv109_01) # check range

### recode highest education attainment of a household
hr_data <- hr_data %>%
  rowwise() %>% # rowwise (household-wise) calculation
  mutate(edu = ifelse(all(is.na(c_across(hv109_01:hv109_56))), NA, # return NA if all NA
                      pmax(c_across(hv109_01:hv109_56), na.rm = TRUE))) # return max value of all columns
hr_data %>% group_by(edu) %>% summarise(n = n()) # check grouping
```

## 5. Join datasets

```{r join}
data <- left_join(ir_data, dplyr::select(hr_data, hv001, hv002, hv005, hv021, hv023, hv012, hv219, edu), 
                       by = c("v001" = "hv001", "v002" = "hv002")) # join by cluster and household numbers
```

## 6. Preparatory

### 6.1 Subset for adolescents

```{r subset}
teendata <- data %>% filter(v013 == 1) # create dataset with only teenagers
```

### 6.2 Create design objects

```{r design}
### survey design for individual level
dhs <- svydesign(id=~v021, strata =~v023, weights=~v005, data=teendata) # create design

### survey design for household level - ***NOT USED***
# dhs_hr <- svydesign(id=~hv021, strata =~hv023, weights=~hv005, data=teendata)
```

## 7. Summary statistics

### 7.1 Sample size

```{r samplesize}
### Sample size individuals and weighted in urban and rural
sumtotal <- data %>% group_by (v025) %>%
  summarise(total = n(), total_weight = round(sum(v005)/1e6,0)) 
sumteen <- data %>% filter (v013 ==1) %>% group_by (v025) %>%
  summarize (teen = n(), teen_weight = round(sum(v005)/1e6,0))
samplesize_ur <- cbind(sumtotal,sumteen[,2:3]) # create dataframe
print(samplesize_ur) # print table

### Sample size individuals and weighted in regions
sumtotal_region <- data %>% group_by (v024) %>%
  summarise(total = n(), total_weight = round(sum(v005)/1e6,0)) 
sumteen_region <- data %>% filter (v013 ==1) %>% group_by (v024) %>%
  summarize (teen = n(), teen_weight = round(sum(v005)/1e6,0))
samplesize_region <- cbind(sumtotal_region,sumteen_region[,2:3]) # create dataframe
print(samplesize_region) # print table

### Sample size for 15-19 who ever had pregnant
round(svytable(~teen_preg + v025, design = dhs)/1e6,0)
```

### 7.2 Teenage pregnancy rate

```{r tprate}
### teenage pregnancy rate in urban and rural
tpr_ur_raw <- svyby(~(teen_preg == 1), ~v025, dhs, svymean, vartype=c("ci"))
tpr_ur <- tpr_ur_raw [,c(1,3,5,7)] # filter for proportion and CI

### teenage pregnancy rate in regions
tpr_region_raw <- svyby(~(teen_preg == 1), ~v024, dhs, svymean, vartype=c("se","ci"))
tpr_region <- tpr_region_raw [,c(1,3)]
print(tpr_region*1000)
# write.csv(tpr_region, "tp_map_region.csv", row.names = T) # to save csv

### teenage pregnancy rate by strata for mapping - urban/rural in each region
tpr_strata_raw <- svyby(~(teen_preg == 1), ~v024 + v025, dhs, svymean, vartype=c("ci"))
tpr_strata <- tpr_strata_raw [,c(1,2,4,6,8)]
tpr_strata <- tpr_strata %>% mutate (tpr = tpr_strata[,3]*100)
# write.csv(tpr_strata, "tp_map.csv", row.names = T) # to save csv
```

### 7.3 Outcome of teenage pregnancy

```{r teenpregoutcome}
# Live birth - 183 never had a live birth
svytable(~teen_preg + birth_gp + v025, design = dhs, na.action = na.pass)
svychisq(~birth_gp + v025, design = dhs, statistics = "design") # chisq for birth_gpvsv025 means number of livebirths against urban/rural

# pregnancy loss - 618 never had a pregnancy loss
svytable(~teen_preg + loss_gp + v025, design = dhs, na.action = na.pass)
svychisq(~loss_gp + v025, design = dhs, statistics = "design") # chisq for loss_gpvsv025 means pregnancy loss against urban/rural
```

## 8. Descriptive statistics, disaggregated by urban and rural

'teendata', which is subset of joined dataset for 15-19 women respondents will be used for descriptive analysis. Design is also set on same dataset, i.e., 'teendata'.

Sample code to correct and round up the numbers in svytables, but I didn't use it to correct myself.

```{r correct table}
#round(your_svytable/1e6,0)
```

### 8.1 **Socio-demographic factors**

```{r sd}
### age
svyby(formula = ~v012, by = ~v025 + teen_preg, design = dhs, FUN = svymean, vartype=c("ci"))
svyttest(v012 ~ v025, design = dhs) # t-test for pvalue

### education
svytable(~edu_gp + v025 + teen_preg, design = dhs)
svychisq(~edu_gp + v025, design = dhs, statistics = "design")

### current marital status
svytable(~marital + v025 + teen_preg, design = dhs)
svychisq(~marital + v025, design = dhs, statistics = "design")

### age at first marriage/union
svyby(formula = ~v511, by = ~v025 + teen_preg, design = dhs, FUN = svymean, vartype=c("ci"),
      na.rm = TRUE) # exlude NA - 2,576 did not respond/never been in a union
svyttest(v511 ~ v025, design = dhs)

### age at first sex
svyby(formula = ~v531, by = ~v025 + teen_preg, design = dhs, FUN = svymean, vartype=c("ci"),
      na.rm = TRUE) # exlude NA - 2,576 did not respond/never been in a union
svyttest(v531 ~ v025, design = dhs)
```

### 8.2 **Current partner's characteristics**

```{r partner}
### partner age
svyby(formula = ~v730, by = ~v025 + teen_preg, design = dhs, FUN = svymean, vartype=c("ci"),
      na.rm = TRUE) # exlude NA - 2,576 did not respond/never been in a union
svyttest(v730 ~ v025, design = dhs)

### partner education status
svytable(~v701 + v025 + teen_preg, design = dhs)
svychisq(~v701 + v025, design = dhs, statistics = "design")
```

### **8.3 Socio-Economic**

```{r sd_household}
### HH wealth index
svytable(~v190 + v025 + teen_preg, design = dhs)
svychisq(~v190 + v025, design = dhs, statistics = "design")

### employment
svytable(~employ_current + v025 + teen_preg, design = dhs)
svychisq(~employ_current + v025, design = dhs, statistics = "design")
```

### 8.4 Health behaviour

```{r hbehaviour}
### wantness (no respondent - 2,982)
svytable(~v225 + v025, design = dhs)
svychisq(~v225 + v025, design = dhs, statistics = "design")

### knoweldge on contraceptive methods
svytable(~contra_know_any + v025 + teen_preg, design = dhs)
svychisq(~contra_know_any + v025, design = dhs, statistics = "design")

### current contraceptive use
svytable(~contra_current + v025 + teen_preg, design = dhs)
svychisq(~contra_current + v025, design = dhs, statistics = "design")

### intention to use contraception in the future
svytable(~contra_future + v025 + teen_preg, design = dhs)
svychisq(~contra_future + v025, design = dhs, statistics = "design")

### access to information about family planning
svytable(~fp_info + v025 + teen_preg, design = dhs)
svychisq(~fp_info + v025, design = dhs, statistics = "design")

### pre or intra or extra marital sex (for teenage pregnancies only)
svytable(~premaritalsex + v025 + teen_preg, design = dhs)
```

### 8.5 Problem with access to health services

```{r problemaccess}
### problem with access to health services - permission to go
svytable(~v467b + v025 + teen_preg, design = dhs)
svychisq(~v467b + v025, design = dhs, statistics = "design")

### problem with access to health services - money needed
svytable(~v467c + v025 + teen_preg, design = dhs)
svychisq(~v467c + v025, design = dhs, statistics = "design")

### problem with access to health services - distance
svytable(~v467d + v025 + teen_preg, design = dhs)
svychisq(~v467d + v025, design = dhs, statistics = "design")

### problem with access to health services - not want to go alone
svytable(~v467f + v025 + teen_preg, design = dhs)
svychisq(~v467f + v025, design = dhs, statistics = "design")
```

### 8.6 Household characteristics

```{r hhcharac}
### household size
svyby(formula = ~hv012, by = ~v025 + teen_preg, design = dhs, FUN = svymean, vartype=c("ci"))
svyttest(hv012 ~ v025, design = dhs)

### highest household education attainment
svytable(~edu + v025 + teen_preg, design = dhs)
svychisq(~edu + v025, design = dhs, statistics = "design")

### sex of household head
svytable(~hv219 + v025 + teen_preg, design = dhs)
svychisq(~hv219 + v025, design = dhs, statistics = "design")
```

### 8.7 Migration

```{r migration}
## recent migration
svytable(~recent_migrate + v025 + teen_preg, design = dhs)

## type of migration (*** for recently migrated only ***)
svytable(~type_migrate + v025 + teen_preg + recent_migrate, design = dhs)
```

## 9. Prepare dataset for regression analysis

'teendata', which is subset of joined dataset for 15-19 women respondents will be used for descriptive analysis. Design is also set on same dataset, i.e., 'teendata'.

### 9.1 Missingness

Firstly, get cascade of values using survey package. Note that numbers may different if survey package is not used. Among total 3,083 (15-59) respondents, 678 are classified as Teenage pregnancy - who ever had pregnant. 2,463 - never married, 564 - currently married, 56 - ended.

```{r getnumbers}
## check numbers
teendata %>% summarise(total_weight = round(sum(v005)/1e6,0))  # number of total sample - 3,083
round(svytotal(~teen_preg==1, design = dhs) / 1e6,0) # number of who ever pregnant (TP) - 678
round(svytotal(~marital==1, design = dhs) / 1e6,0) # currently married - 564
round(svytotal(~marital==2, design = dhs) / 1e6,0) # ended married - 56
round(svytotal(~marital==0, design = dhs) / 1e6,0) # never married - 2463
round(svytotal(~v213==1, design = dhs) / 1e6,0) # currently pregnant - 186

```

Then, columns with missing values are explored. Please be noted that not all columns are used in the analysis.

```{r missingness}
## check columns with NA
na_list <- colnames(teendata)[colSums(is.na(teendata)) > 0] 

## NA details
for (col in na_list) {
  na_count <- sum(is.na(teendata[[col]]))
  cat("Variable", col, "> NAs", na_count, "\n")
}
```

**v225 -** questions about current pregnancy with 2,982 NAs. Given that 2,898 are not currently pregnant. **Finding:** No NA among 'currently pregnant' \> no missing. In analysis, to filter only those who are currently pregnant.

```{r na_currentpregnant}
table(teendata$v213, teendata$v225, useNA = "always") # no missing variable
round(svytable(~v213 + v225 + v025, design = dhs, na.action = na.pass)/1e6,0) 
```

**v362/contra_future -** Not used, coded into other variable. Question asked to those who are not currently using contraceptive AND who are currently married.

```{r na_contrafuture}
table(teendata$contra_current, teendata$contra_future, useNA = "always") # can't identify exact numbers
round(svytable(~contra_future + v025, design = dhs, na.action = na.pass)/1e6,0) # this table is used to calculate n in table
```

**v701, v730 -** questions about partners with 2,631 NAs. Given that 2,519 (2,463 - never and 56 - ended) are not currently married. **Finding:** NA among 'currently married' is neglegible amount. In analysis, to filter only those who are currently married.

```{r na_maritalrelated}
# education
table(teendata$marital, teendata$v701, useNA = "always") # can see all never/ended married are NA, and some NA from married
round(svytable(~marital + v701, design = dhs, na.action = na.pass)/1e6,0) # n = 560

# age
table(teendata$marital, teendata$v730, useNA = "always") #
round(svytable(~marital + v730, design = dhs, na.action = na.pass)/1e6,0) # n = 564 
```

**v531, v511 -** questions about age at first sex and age at first marriage. Given that 2,519 (2,463 - never and 56 - ended) are not currently married. **Finding:** NA among 'currently/ended married' is neglegible amount. In analysis, to filter only those who are currently married.

```{r checks}
table(teendata$marital, teendata$v511, useNA = "always") # can see all NA from never got married
table(teendata$marital, teendata$v531, useNA = "always") # most NA from never got married
```

**p32 -** questions about age pregnancy outcomes. **Finding:** No missing detected

```{r na_pregorder}
### p32 - questions about pregnancy outcome againsts livebirths
table(teendata$birth_gp, teendata$p32_01, useNA = "always") # first preg - all NA are never had a child birth_gp = 0 > no missing
table(teendata$birth_gp, teendata$p32_02, useNA = "always") # second preg - all NA birth_gp = 0 or 1 > no missing
table(teendata$birth_gp, teendata$p32_03, useNA = "always") # third preg - all NA birth_gp = 0,1,2 > no missing
table(teendata$birth_gp, teendata$p32_04, useNA = "always") # fourth preg - all NA birth_gp = 0,1,2,3 > no missing
table(teendata$birth_gp, teendata$p32_05, useNA = "always") # no one has fith preg

### p32 - questions about pregnancy outcome againsts pregnancy loss
table(teendata$loss_gp, teendata$p32_01, useNA = "always") # all NA are among who never loss pregnancy
```

**edu** - when checking un-weighted data, 48 out of 3,142 records about edu are NAs. **Finding** - Will use complete case

```{r na_edu}
table (teendata$edu, teendata$teen_preg, useNA = "always") # 48 NAs (44 - No TP; 4 - TP)
table (teendata$edu, teendata$v025, useNA = "always") # 48 NAs (23 - Urban; 25 - Rural)
```

### 9.2 Subset final dataset, so that can omit NAs for regression

```{r finalsubset}
# final subset for models
finaldata <- teendata %>% dplyr::select (c(
  v005, v021, v023, # for design
  teen_preg, # outcome 
  v025, # exposure
  v024, # region
  v012,edu_gp,marital,  # socio demographic - age, education, marital,
  v190,employ_current, # socio economnic - wealth, employment,
  contra_know_any, fp_info, # health behaviour - knowledge contraceptive, heard about FP messages
  v467b,v467c,v467d,v467f, # problem access to services - permission, money, distance, alone
  hv012, hv219, edu, # hh characteristics - HH size, sex of hh head, highest edu in hh, 
  v701, v730, v531, v511, contra_current, # for univarite - partner education, partner age, age at first sex, age at first marriage, contraceptive use
  premaritalsex, # sex premarital, marital or extramarital
  recent_migrate, type_migrate # migration status
))

# relevel 4 problem to access variables
finaldata$v467b <- relevel(factor(finaldata$v467b), ref = "2")
finaldata$v467c <- relevel(factor(finaldata$v467c), ref = "2")
finaldata$v467d <- relevel(factor(finaldata$v467d), ref = "2")
finaldata$v467f <- relevel(factor(finaldata$v467f), ref = "2")

# factorize 
finaldata$teen_preg <- factor(finaldata$teen_preg)
```

```{r finaldesign}
dhsfinal <- svydesign(id = ~v021, strata = ~v023, weights = ~v005, data = finaldata)
```

## 10. Regression

### 10.1 Bivariate

```{r bivariate}
# v025: urban rural
model_v025 <- svyglm(teen_preg ~ factor(v025),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v025)[2]))
print (exp (confint(model_v025)[2, ]))
print (summary(model_v025)$coefficients[2,"Pr(>|t|)"])

# v024: regions
model_v024 <- svyglm(teen_preg ~ factor(v024),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v024)))
print (exp (confint(model_v024)))
print (summary(model_v024)$coefficients[,"Pr(>|t|)"])

# v012: age (Note: older girls have higher chance to get pregnant naturally)
model_v012 <- svyglm(teen_preg ~ v012,
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v012)[2]))
print (exp (confint(model_v012)[2, ]))
print (summary(model_v012)$coefficients[2,"Pr(>|t|)"])

# v106: education
model_edu <- svyglm(teen_preg ~ factor(edu_gp),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_edu)))
print (exp (confint(model_edu)))
print (summary(model_edu)$coefficients[,"Pr(>|t|)"])

# marital: marital status
model_marital <- svyglm(teen_preg ~ factor(marital),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_marital)))
print (exp (confint(model_marital)))
print (summary(model_marital)$coefficients[,"Pr(>|t|)"])

# recent_migrate: Migration withing previous 5 years
model_migrate <- svyglm(teen_preg ~ factor(recent_migrate),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_migrate)))
print (exp (confint(model_migrate)))
print (summary(model_migrate)$coefficients[,"Pr(>|t|)"])

# v190: HH wealth index
model_v190 <- svyglm(teen_preg ~ factor(v190),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v190)))
print (exp (confint(model_v190)))
print (summary(model_v190)$coefficients[,"Pr(>|t|)"])

# employ_current: Current employment status
model_employ_current <- svyglm(teen_preg ~ factor(employ_current),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_employ_current)[2]))
print (exp (confint(model_employ_current)[2, ]))
print (summary(model_employ_current)$coefficients[2,"Pr(>|t|)"])

# contra_know_any: knowledge on contraceptive methods
model_contra_know_any <- svyglm(teen_preg ~ factor(contra_know_any),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_contra_know_any)[2]))
print (exp (confint(model_contra_know_any)[2, ]))
print (summary(model_contra_know_any)$coefficients[2,"Pr(>|t|)"])

# fp_info: Heard about family planning message
model_fp_info <- svyglm(teen_preg ~ factor(fp_info),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_fp_info)[2]))
print (exp (confint(model_fp_info)[2, ]))
print (summary(model_fp_info)$coefficients[2,"Pr(>|t|)"])

# v467b: Problem in 'getting permission' to access health services
model_v467b <- svyglm(teen_preg ~ factor(v467b),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v467b)[2]))
print (exp (confint(model_v467b)[2, ]))
print (summary(model_v467b)$coefficients[2,"Pr(>|t|)"])

# v467c: Problem in 'money needed' to access health services
model_v467c <- svyglm(teen_preg ~ factor(v467c),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v467c)[2]))
print (exp (confint(model_v467c)[2, ]))
print (summary(model_v467c)$coefficients[2,"Pr(>|t|)"])

# v467d: Problem in 'distance' to access health services
model_v467d <- svyglm(teen_preg ~ factor(v467d),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v467d)[2]))
print (exp (confint(model_v467d)[2, ]))
print (summary(model_v467d)$coefficients[2,"Pr(>|t|)"])

# v467f: Problem in 'not want to go alone' to access health services
model_v467f<- svyglm(teen_preg ~ factor(v467f),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v467f)[2]))
print (exp (confint(model_v467f)[2, ]))
print (summary(model_v467f)$coefficients[2,"Pr(>|t|)"])

# hv012: Size of household
model_hv012<- svyglm(teen_preg ~ hv012,
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_hv012)[2]))
print (exp (confint(model_hv012)[2, ]))
print (summary(model_hv012)$coefficients[2,"Pr(>|t|)"])

# hv219: Sex of household head - reference = 1 male
model_hv219<- svyglm(teen_preg ~ factor(hv219),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_hv219)[2]))
print (exp (confint(model_hv219)[2, ]))
print (summary(model_hv219)$coefficients[2,"Pr(>|t|)"])
```

Couldn't calculate p-value for following bivariate models

```{r bivariate_need na.omit data}
# edu: Highest education attainment in a HH
model_hhedu <- svyglm(teen_preg ~ factor(edu),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_hhedu)))
print (exp (confint(model_hhedu)))
coef_se <- sqrt(diag(vcov(model_hhedu))) 
2 * (1 - pnorm(abs(coef(model_hhedu)[2:6] / coef_se[2])))
# print (summary(model_hhedu)$coefficients[2:5,"Pr(>|t|)"])

# v730: age
model_v730<- svyglm(teen_preg ~ v730,
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v730)[2]))
print (exp (confint(model_v730)[2,]))
coef_se <- sqrt(diag(vcov(model_v730))) # get se
2 * (1 - pnorm(abs(coef(model_v730)[2] / coef_se[2]))) # calculate p-value based on the z-statistic.

# v701: Partners education
model_v701<- svyglm(teen_preg ~ factor(v701),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v701)))
print (exp (confint(model_v701)))
coef_se <- sqrt(diag(vcov(model_hhedu))) 
2 * (1 - pnorm(abs(coef(model_hhedu)[2:3] / coef_se[2]))) # pvalue from se

# v531: Age at first sex
model_v531 <- svyglm(teen_preg ~ v531,
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v531)[2]))
print (exp (confint(model_v531)[2, ]))
coef_se <- sqrt(diag(vcov(model_v531))) # get se
2 * (1 - pnorm(abs(coef(model_v531)[2] / coef_se[2]))) # calculate p-value based on the z-statistic.

# v511: Age at first marriage/union
model_v511 <- svyglm(teen_preg ~ v511,
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_v511)[2]))
print (exp (confint(model_v511)[2, ]))
coef_se <- sqrt(diag(vcov(model_v511))) # get se
2 * (1 - pnorm(abs(coef(model_v511)[2] / coef_se[2]))) # calculate p-value based on the z-statistic.

# contra_current: Current contraceptive use
model_contra_current <- svyglm(teen_preg ~ factor(contra_current),
                    design = dhsfinal, family = binomial(), na.action = na.exclude)
print (exp (coef(model_contra_current)[2]))
print (exp (confint(model_contra_current)[2, ]))
coef_se <- sqrt(diag(vcov(model_contra_current))) 
2 * (1 - pnorm(abs(coef(model_contra_current)[2] / coef_se[2]))) # pavlue from se
```

### 10.2 Multiple variable logistic regression

Prepare dataset by excluding variables with \<0.1 p-value in bivariate analysis, and variables only for a subset of sample (e.g., questions only for married women). And create design for survey package.

```{r subsetdata_glm, warning =FALSE}
# final subset for models
glmdata <- finaldata %>% dplyr::select (c(
  v005, v021, v023, # for design
  teen_preg, # outcome 
  v025, # exposure
  v024, # region
  v012,edu_gp,marital,  # socio demographic - age, education, marital,
  v190,employ_current, # socio economnic - wealth, employment,
  contra_know_any, fp_info, # health behaviour - knowledge contraceptive, heard about FP messages
  v467c,v467f, # problem access to services - money, alone
  edu # hh characteristics - highest edu in hh, 
))

# Omit na values from dataset
glmdata <- na.omit(glmdata) # 48 observations are deleted

# create survey design for glm
glmdesign <- svydesign(id = ~v021, strata = ~v023, weights = ~v005, data = glmdata)
```

Forward approach:

-   Model 1: Socio-demographic - age, education, marital status

```{r model1, warning=FALSE}
# age, education, marital status
modelm_1 <- svyglm(teen_preg ~ factor(v025) + 
                     v012 + factor (edu_gp) + factor (marital),
                   design = glmdesign, family = binomial(), na.action = na.exclude)

print (exp (coef(modelm_1)))
print (exp (confint(modelm_1)))
print (summary(modelm_1)$coefficients[,"Pr(>|t|)"])
```

-   Model 2: Model 1+ Socio-economic - wealth index, employment

```{r model2, warning=FALSE}
# wealth index, employment
modelm_2 <- svyglm(teen_preg ~ factor(v025) + 
                     v012 + factor (edu_gp) + factor (marital) + 
                     factor (v190) + factor (employ_current), 
                   design = glmdesign, family = binomial(), na.action = na.exclude)

print (exp (coef(modelm_2)))
print (exp (confint(modelm_2)))
print (summary(modelm_2)$coefficients[,"Pr(>|t|)"])
```

-   Model 3: Model 2 + Health behaviour - knowledge on contraceptive, heard family planning

```{r model3}
# knowledge on contraceptive, heard family planning
modelm_3 <- svyglm(teen_preg ~ factor(v025) + 
                     v012 + factor (edu_gp) + factor (marital) + 
                     factor (v190) + factor (employ_current) +
                     factor (contra_know_any) + factor (fp_info),
                   design = glmdesign, family = binomial(), na.action = na.exclude)

print (exp (coef(modelm_3)))
print (exp (confint(modelm_3)))
print (summary(modelm_3)$coefficients[,"Pr(>|t|)"])
```

-   Model 4: Model 3 + Problem with access to services - all 4

```{r model4}
# permission, money, distance, alone
modelm_4 <- svyglm(teen_preg ~ factor(v025) + 
                     v012 + factor (edu_gp) + factor (marital) + 
                     factor (v190) + factor (employ_current) +
                     factor (contra_know_any) + factor (fp_info) +
                     factor (v467c) +factor (v467f),
                   design = glmdesign, family = binomial(), na.action = na.exclude)

print (exp (coef(modelm_4)))
print (exp (confint(modelm_4)))
print (summary(modelm_4)$coefficients[,"Pr(>|t|)"])
```

-   Model 5: Model 4 + HH characteristics - hh size, sex of hh head

```{r model5, warning=FALSE}
# hh size, sex of hh head
modelm_5 <- svyglm(teen_preg ~ factor(v025) + 
                     v012 + factor (edu_gp) + factor (marital) + 
                     factor (v190) + factor (employ_current) +
                     factor (contra_know_any) + factor (fp_info) +
                     factor (v467c) +factor (v467f) +
                     factor (edu),
                   design = glmdesign, family = binomial())

print (exp (coef(modelm_5)))
print (exp (confint(modelm_5)))
print (summary(modelm_5)$coefficients[,"Pr(>|t|)"])
```

### 10.3 Check multicolinearity by VIF

The full model is checked for multicolinearity using adjusted Generalized Variance Inflation Factors (GVIF).

```{r VIF}
# Calculate VIF values to check high adjusted GVIF values (>5)
car::vif(modelm_5)
```

### 10.4 Check assumptions

```{r checkassumptions}
par(mfrow = c(2, 2))
plot(modelm_5)
```

### 10.5 Model fitting

**Attempt 1:** Remove outliers, log transformation and taking out not significant variables: **AIC reduced from 1,699.57 in full model (modelm_5) to 1,559.18 after removing outliers.**

```{r modelfit}
# check 10 outliers *** only after generating model ***
plot(modelm_5, which = 4, id.n = 10) 

# remove outliers
fitdata <- glmdata [- c(70,442,505,607,1680,1777,1781,1850,1996,2002),]

# create design using fitdata
dhsfit <- svydesign(id = ~v021, strata = ~v023, weights = ~v005, data = fitdata)

# develop model
modelfit <- svyglm(teen_preg ~ factor(v025) + 
                     v012 + factor (edu_gp) + factor (marital) + 
                     factor (v190) + factor (employ_current) +
                     factor (contra_know_any) + factor (fp_info) +
                     factor (v467c) +factor (v467f) +
                     factor (edu),
                   design = dhsfit, family = binomial(),
                   na.action = na.exclude)

# diagnose model
plot(modelfit)

# testing summ package for summary and forest plot
## summarizing, can check colinearlity* together (*be cautious to interpret high VIF values within same categorical variables)
summ(modelfit, vifs = TRUE) # AIC 1559.18 
summ(modelm_5, vifs = TRUE) # AIC 1699.57
```

**Attempt 2:** Alternative dataset - using only married. AIC is greatly reduced to 1,159, but the purpose of our analysis for teenage pregnancy regardless of marital status. So, **we will not use this model** since it will censor information about adolescent who are not in a marriage/union.

```{r alternative}
# remove married
marrydata <- glmdata %>% filter (marital != 1)
dim(marrydata)
# marrydata <- marrydata [- c(1404,55,1488,1434,2201,1521),] # no difference

# create design using fitdata
dhsmarry <- svydesign(id = ~v021, strata = ~v023, weights = ~v005, data = marrydata)

# develop model
modelmarry <- svyglm(teen_preg ~ factor(v025) + 
                     v012 + factor (edu_gp) + factor (marital) + 
                     factor (v190) + factor (employ_current) +
                     factor (contra_know_any) + factor (fp_info) +
                     factor (v467c) +factor (v467f) +
                     factor (edu),
                   design = dhsmarry, family = binomial(),
                   na.action = na.exclude)

# diagnose model
plot(modelmarry)

# testing summ package for summary and forest plot
## summarizing, can check colinearlity* together (*be cautious to interpret high VIF values within same categorical variables)
summ(modelmarry, vifs = TRUE) # AIC 1159.30
summ(modelm_5, vifs = TRUE) # AIC 1699.57
```

**Attempt 3:** We use stepAIC as Tutor suggested. From the forward approach to both full model (modelm_5) and fit model (10 ouliers excluded), no variables has been taken out from this process. So, not improvement could be made.

```{r stepAIC, warning=FALSE}
# apply stepwise regression (forward) for full model (modelm_5)
stepfull <- stepAIC(modelm_5, direction = "forward")
stepfull$anova # compare initial and final model

# apply stepwise regression (forward) for fitted model (modelfit)
stepfit <- stepAIC(modelfit, direction = "forward")
stepfit$anova # compare initial and final model

# see the results 
stepfull$deviance; stepfit$deviance # compare deviance >1
stepfull$aic; stepfit$aic # compare aic
```

**Final decision**: AIC value compromises both fit and complexity, so we choose model based on its AIC. Fitted model has lower AIC of 1,559 when full model has 1,700. AUC is another performance perspective to evaluate model. Fit model has 91.2% (95% CI 0.90 - 0.92) accuracy while full model has slightly lower accuracy of 90.7%. So, we will choose fitted model (modelfit) as our logistic regression model.

```{r decision}
# comparing deviance and aic
modelm_5$deviance; modelfit$deviance # 1663.45 vs 1526.331 - loss greately improved when outliers are removed
modelm_5$aic; modelfit$aic # 1699.573 vs 1559.184 

# comparing accuracy
## full model preprocess
predfull <- predict(modelm_5, glmdata, type = "response") 
predfull <- as.factor(ifelse(predfull >= 0.5, 1, 0))
## fit model preprocess
predfit <- predict(modelfit, fitdata, type = "response") 
predfit <- as.factor(ifelse(predfit >= 0.5, 1, 0))
## compare two confusion matrix
confusionMatrix(predfull,glmdata$teen_preg, positive = "1")
confusionMatrix(predfit,fitdata$teen_preg, positive = "1")

# get values from our final model
print (exp (coef(modelfit)))
print (exp (confint(modelfit)))
print (summary(modelfit)$coefficients[,"Pr(>|t|)"])
```
